\Large{Research Seminar Software Science} \\ \huge{Simulation of monadic effects in Haskell}

### 2018-05-29 paper.tex
started with alternation section

    Applying this parser to an input string ``12rera" will succeed with the result [((`1', `2'), ``rera")] whereas in case of an input ``1rera" will fail and return [ ] since the second parsed character \textit{`r'} is not a digit. \\ \\
    Nevertheless, it would not be convenient to create new parsers each time more items need to be parsed. For that reason, \textit{recursive parsers} are desired. Additionally, recursive operation must be terminated at some point. In order to achieve or not termination, the \textbf{alternation} combinator has to be used but more on that on the next subsection.

    \subsubsection{Alternation}

    \begin{thebibliography}{9}
    \bibitem{categorytheory} 
    M. D. Hill, Jonathan & Clarke, Keith. (1994). \textit{An Introduction to Category Theory, Category Theory Monads, and Their Relationship to Functional Programming}.
    \bibitem{essenceFP}
    Wadler, P. (1992b). \textit{The essence of functional programming. In
    20th ACM Symposium on Principles of Programming Languages}
    (POPL’92), pages 1–14. ACM, Albuquerque.
    \bibitem{original}
    Walder, P. \textit{Monads for functional programming}, section 5.2. University of Glasgow. 
    \bibitem{pearls}
    Hutton, G. and Meijer, E. \textit{Monadic Parsing in Haskell}. University of Nottingham.
    \bibitem{bringMonadComprehension}
    Giorgidze. G, Grust. T, Schweinsberg. N, and Weijers. J. \textit{Bring Back Monad Comprehensions}. Wilhelm-Schickard-Institut fur Informatik and Eberhard Karls Universitat Tubingen.
    \end{thebibliography}
    \end{document}

>>>>

    Applying this parser to an input string ``12rera" will succeed with the result [((`1', `2'), ``rera")] whereas in case of an input ``1rera" will fail and return [ ] since the second parsed character \textit{`r'} is not a digit. \\ \\
    Nevertheless, it would not be convenient to create new parsers each time more items need to be parsed. For that reason, \textit{recursive parsers} are desired. Additionally, recursive operation must be terminated at some point. In order to achieve or not termination, the \textbf{alternation} combinator has to be used but more on that on the next subsection.
    \subsubsection{Alternation}

    In this subsection, the attention will be redirected towards producing alternation in parsers. Additionally, it will be assumed that the parser will exhibit non-deterministic behavior. Hence, employing two parsers in alternation will demand the initial to be applied to the input and if it fails to parse anything then the consecutive parser will be applied to the same input.
    \begin{thebibliography}{9}
    \bibitem{categorytheory} 
    M. D. Hill, Jonathan & Clarke, Keith. (1994). \textit{An Introduction to Category Theory, Category Theory Monads, and Their Relationship to Functional Programming}.
    \bibitem{essenceFP}
    Wadler, P. (1992b). \textit{The essence of functional programming. In
    20th ACM Symposium on Principles of Programming Languages}
    (POPL’92), pages 1–14. ACM, Albuquerque.
    \bibitem{original}
    Walder, P. \textit{Monads for functional programming}, section 5.2. University of Glasgow. 
    \bibitem{pearls}
    Hutton, G. and Meijer, E. \textit{Monadic Parsing in Haskell}. University of Nottingham.
    \bibitem{bringMonadComprehension}
    Giorgidze. G, Grust. T, Schweinsberg. N, and Weijers. J. \textit{Bring Back Monad Comprehensions}. Wilhelm-Schickard-Institut fur Informatik and Eberhard Karls Universitat Tubingen.
    \end{thebibliography}
    \end{document}
